%-----------------------------------------
% Michael Wright
% Resumé
%
% URL: http://github.com/mdwrigh2/resume
% This document is covered under the Creative Commons Attribution 3.0 Unported License
%-----------------------------------------

%!TEX TS-program = xelatex
%!TEX encoding = UTF-8 Unicode

\documentclass[margin]{res}
\usepackage{fontspec}

% DOCUMENT LAYOUT
\setlength{\textwidth}{5.1in}
\newsectionwidth{1in}

% FONTS
% FONTS
\defaultfontfeatures{Mapping=tex-text} % converts LaTeX specials (``quotes'' --- dashes etc.) to unicode

% Remove % to set to different fonts
%\setromanfont [Ligatures={Common},Numbers={OldStyle}]{Adobe Caslon Pro}
%\setmonofont[Scale=0.8]{Monaco} 

% ---- CUSTOM AMPERSAND
\newcommand{\amper}{{\fontspec[Scale=.95]{Adobe Caslon Pro}\selectfont\itshape\&}}

% ---- MARGIN YEARS
%\newcommand{\years}[1]{\marginpar{\scriptsize #1}}

% HEADINGS
%\usepackage{sectsty} 
%\usepackage[normalem]{ulem} 
%\sectionfont{\rmfamily\mdseries\Large} 
%\subsectionfont{\rmfamily\mdseries\scshape\normalsize} 
%\subsubsectionfont{\rmfamily\bfseries\upshape\normalsize} 

% PDF SETUP
% ---- FILL IN HERE THE DOC TITLE AND AUTHOR
\usepackage[dvipdfm, bookmarks, colorlinks, breaklinks, pdftitle={Michael Wright Resume},pdfauthor={Michael Wright}]{hyperref}  
\hypersetup{linkcolor=blue,citecolor=blue,filecolor=black,urlcolor=blue} 

\begin{document}



% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf Michael D. Wright}
% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
 \moveleft.5\hoffset\centerline{9500 Kingsford Dr.}
 \moveleft.5\hoffset\centerline{Cary, NC 27518}
 \moveleft.5\hoffset\centerline{(919) 656-4962}
 \moveleft.5\hoffset\centerline{mdwrigh2@ncsu.edu}
 
 \begin{resume}
 
\section{\sc Objective} To further myself as a computer scientist and programmer by participating in the architecture and development of interesting software projects and research.
 

\section{\sc Education} {\sl Bachelor of Science,} \\
                      % \sl will be bold italic in New Century Schoolbook (or
	              % any postscript font) and just slanted in
		      %	Computer Modern (default) font
                North Carolina State University, Raleigh, NC, 
                expected May 2012 \\
                Concentration: Computer Science and Mathematics \\
                GPA: 3.994 \\
                CSC GPA: 4.0 \\
                MA GPA: 4.0
\section{\sc Relevant \\ Courses} Operating Systems \\
                                  Data Structures and Algorithms \\
                                  C and Software Tools \\
                                  Software Engineering
 
 
\section{\sc Computer \\ Skills} {\sl Languages:} Ruby, C, Python, Java\\
	       {\sl Software:} Git, Subversion, Apache, Passenger, MySQL, Capistrano, Mongrel, Monit, Chef, \LaTeX \\
                {\sl Operating Systems:} Windows, Windows Server (previous experience with Small Business Server 2003), OS X, Linux (Primarily Debian-based distributions), Xen, VMWare Server ESXi. \\
                {\sl Development Styles:} Experienced in both waterfall and agile development methodologies.
 
\section{\sc Experience} 
    {\sl Research Assistant} \hfill Summer 2010 - Current \\
    North Carolina State University
    With Dr. Jiang and the Systems Security Group
    \begin{itemize} \itemsep -2pt % reduce space between items
      \item 
    \end{itemize}
    {\sl Junior Developer/IT Intern} \hfill Summer 2008 - Spring 2010 \\
		Futures Inc., Durham, NC
    \begin{itemize}  \itemsep -2pt %reduce space between items
        \item Aided in the design, and provided the implementation and support of a large scale (10,000+ initial users), Xen-virtualized server environment housing a rich internet web application.
        \item   Solely responsible for office network hardware, installation and support.  

	      \item Continually assessed the needs of the rapidly growing organization in order to ensure high availability and reliability. 
	      \item Gained software development experience via the completion of individual projects.
        \item Aided in the transfer from rented hardware running Xen instances, to
              Engine Yard's Amazon EC2-based cloud computing service.
    \end{itemize}
    {\sl Network Cabling Apprentice} \hfill            Summer 2007 \\
    Trident Technology Solutions
    \begin{itemize}  \itemsep -2pt %reduce space between items
      \item Built server racks, mounted cable trays, and ran cables within newly built data centers.
    \end{itemize} 
 
\section{\sc Honors}
  Volunteer for CarolinaCon, a regional technology conference from 2005 - 2007\\
  Dean's List all semesters
  Active Member of the NCSU Linux User Group
  Contributor to open source projects - see http://github.com/mdwrigh2

 

\end{resume}
\end{document}



